---
title: "regression_analysis"
output: html_document
date: "2023-04-06"
---

```{r}
#install.packages('corrplot')
#install.packages('xts')
library(corrplot)
library(xts)
library(vctrs)
library(rlang)
library(kernlab)
library(crypto2)
library('lubridate')
library('dplyr')
library(reshape2)
library(glue)
library(qcc)
library(tidyverse)
library(data.table)
library(ggplot2)
```

```{r}
data.daily <- read.csv('../Data/data_daily.csv')[,-1]
data.hourly <- read.csv('../Data/data_hourly.csv')[,-1]
```

```{r}
head(data.daily)
head(data.hourly)
```

Now, lets drop the rows that have no information in the close column (due to the missing price data in the twitter input data. This was addressed in the data prep Rmd file.)

```{r}

data.hourly <-data.hourly[is.na(data.hourly$close) == F,]

data.hourly$datetime <- ymd_hms(data.hourly$datetime)
data.hourly$day <- ymd(data.hourly$day)

data.daily$day <- ymd(data.daily$day)
```

# Data Analysis

As part of our analysis, we want to try different time-shifting intervals. i.e. does the price of bitcoin at time *t* depend on the sentiment at time *t-n* where n is the number of period back we shift. To faciliate this, we will write a function that takes in a dataframe, and shifts the closing price of bitcoin backwards *n* periods, and returns a new data frame. This way, when we look at one row of data, we can see how the sentiment of reddit comments and tweets impact the price n periods from now.

```{r}
shift_df <- function(df, n){
  dfc <- data.table(copy(df))
  cols = c("close")
  anscols = paste("lead", cols, sep="_")

  dfc[order(day), (anscols) := shift(.SD, n, type="lead"), .SDcols=cols]
  dfc <- dfc %>% mutate(price_dif = lead_close - close)
  dfc <- dfc %>% mutate(price_dif_percent = round((lead_close/close) - 1,4))
  dfc <- dfc %>% mutate(price_dir = ifelse(price_dif >=0, 1,0))
  dfc <- dfc[1:(nrow(dfc)-n),]
  dfc
  
}

```

# Plotting some data

First, lets write a function that takes in a the columns we want to chart, scales them to have a mean of 0 and standard deviation of 1, and plots them against each other.

```{r}
plot_scaled_data <- function(df, y_cols, x_col, title, t){
  
  df<- data.frame(df)
  
  df[,y_cols] <- scale(df[,y_cols])
  df <- cbind(df[,x_col],df[,y_cols])
  colnames(df)[1] <- x_col
  df <- data.table(df)
  df <- melt(df, id.vars = x_col)
  plt <- ggplot(df,
                aes(x = .data[[x_col]], y = value, color = variable)) + 
         ggtitle(title)
  
  if (t == 'line') {
    plt = plt + geom_line()
  } else if (t == 'scatter'){
    plt = plt + geom_point() 
    
  }
  plt
}
```

## Sentiment Rating (Tweets) vs. Price

```{r}
cols <- c('Sent_positives',
          "sent_negatives",
          'close'
          )
data.daily$day <- ymd(data.daily$day)
plot_scaled_data(data.daily, cols, 'day', 'Sent Rating vs. Price', 'line')
#data.daily[,cols]
```

## Sentiment mix vs. Price

```{r}
df <- data.daily


cols <- c('percent_pos_reddit',
          "percent_pos_twitter",
          'percent_neg_reddit',
          'percent_neg_twitter',
          'close')
plot_scaled_data(data.daily, cols, 'day', 'Sentiment Mix vs. Price (Scaled, Daily)', 'line')



df <- data.hourly
cols <- c('percent_pos_reddit',
          "percent_pos_twitter",
          'percent_neg_reddit',
          'percent_neg_twitter',
          'close')
plot_scaled_data(df, cols, 'datetime', 'Sentiment Mix vs. Price (Scaled, Hourly)', 'line')
```

Visually inspecting this, it does not appear that the mix of positive/negative comments/tweets appears to fluctuate in any meaningful way with the price. We expected to see that when price is climing, the percent mix of positive comments/Tweets about bitcoin would also increase. However, this was not the case.

## \# of Comments/Tweets vs. Price

```{r}

df <- data.daily
cols <- c('total_reddit',
          "positive_reddit",
          'negative_reddit',
          'close')
plot_scaled_data(df, cols, 'day', 'Reddit Comments vs. Price (Scaled, Daily)', 'line')

cols <- c('total_tweets',
          "positive_tweets",
          'negative_tweets',
          'close')
plot_scaled_data(df, cols, 'day', 'Tweets vs. Price (Scaled, Daily)', 'line')


df <- data.hourly

cols <- c('total_reddit',
          "positive_reddit",
          'negative_reddit',
          'close')
plot_scaled_data(df, cols, 'datetime', 'Reddit Comments vs. Price (Scaled, Hourly)', 'line')

cols <- c('total_tweets',
          "positive_tweets",
          'negative_tweets',
          'close')
plot_scaled_data(df, cols, 'datetime', 'Tweets vs. Price (Scaled, Hourly)', 'line')
```

These charts are particularly interesting, it seems that the total number of tweets and comments, regardless of whether they are positive or negative, seems to very closely track the price of bitcoin. Let's plot the total tweet/comment activity against the price of bitcoin on each day/hour and see if there appears to be any correlation.

```{r}
df <- data.daily
cols <- c('total_reddit',
          "positive_reddit",
          'negative_reddit',
          'total_tweets',
          "positive_tweets",
          'negative_tweets'
          )
plot_scaled_data(df, cols, 'close', 'Reddit Comments vs. Price (Scaled, Daily)', 'scatter')

df <- data.hourly
cols <- c('total_reddit',
          "positive_reddit",
          'negative_reddit',
          'total_tweets',
          "positive_tweets",
          'negative_tweets'
          )
plot_scaled_data(df, cols, 'close', 'Reddit Comments vs. Price (Scaled, Daily)', 'scatter')
```

There seems to be a very noticeable correlation between the converation activity and the price of Bitcoin. We will want to explore this in our regression analysis.

## \# of Comments/Tweets vs. Price Changes

Because we are now looking at changes in the price from time t-1 to time t, we will use a scatter plot rather than a line graph. That is because our data is no longer a time series, i.e. the price change in one period is independent of the price change in the previous.

```{r}

#Start by shifting the close price n periods
df <- shift_df(data.daily, 1)[1:nrow(data.daily),]

cols <- c('total_reddit',
          "positive_reddit",
          'negative_reddit',
          'total_tweets',
          "positive_tweets",
          'negative_tweets')
plot_scaled_data(df, cols, 'price_dif_percent', 'Comments/Tweets vs. Price Change (Scaled, Daily), Daily', 'scatter')


df <- shift_df(data.hourly, 1)

cols <- c('total_reddit',
          "positive_reddit",
          'negative_reddit',
          'total_tweets',
          "positive_tweets",
          'negative_tweets')
plot_scaled_data(df, cols, 'price_dif_percent', 'Total Comments/Tweets vs. Price Change, (Scaled, Hourly)', 'scatter')
```

## 
